---
title: "Cognitive Psychology Seminar - Inhibition"
author: "David I., L. V., L. P., S. R"
date: '`r Sys.Date()`'
output:
  html_document:
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_float: yes
    df_print: paged
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, cache = F)
```


```{r packages, include=FALSE }
# Check if packages are installed, if not install and load them

## Make list of required packages 

list.of.packages <- c("dplyr","psych","ggplot2","tidyr","mvnormtest","car","reshape2","tidyverse","afex","lsmeans","ez")

## compare installed and required packages

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

# installed the not yet installed but required packages and load them

if(length(new.packages)) install.packages(new.packages,dependencies = TRUE)
sapply(list.of.packages, require, character.only = TRUE)
```


Read in data files

```{r,readInData}
data_path <- "./Daten/"
files     <- list.files(data_path)
data      <- list()

for(f in files){
  data[[f]] <- read.table(paste0(data_path,f), stringsAsFactors = FALSE,header=TRUE)
  
  if(f=="StopSignal_1802_bed1_vp13.txt"){
    data[[f]]$vp <- 13
  }
}

inhib <- bind_rows(data)
```


```{r,showHead}
inhib

filter(inhib, stop == 1)
```

# Participants

```{r,extractDemoVars}

demo <- inhib %>% dplyr::select(.,vp,alt,ges,std)  %>% group_by(.,vp)  %>%   
  summarise(age    = mean(alt, na.rm = T),
            gender = mean(ges, na.rm = T),
            std    = mean(std, na.rm = T)) %>% 
  mutate(., gender.f = factor(gender,label=c("male","female","NA"),levels=c(1,2,9)), 
            std.f    = factor(std,label=c("psychology","erziehungswiss","lehramt","other","NA"),
                       levels = c(1,2,3,4,9)))

```

### Gender

```{r,gender}

      table(demo$gender.f)
      table(demo$gender.f)/nrow(demo)
```

### Age

```{r,age}

      psych::describe(demo$age) %>% knitr::kable(.)
      hist(demo$age)
```

### Course of Study

```{r,cos}

      table(demo$std.f)
      table(demo$std.f)/nrow(demo)
```


# Experiment

## Variable Label and Values

Variable      | Description                 | Values & Labels 
------------- | --------------------------  | ---------------------------------------
vp            | VPN ID                      | Nominal 1-22
alt           | Age                         | Integer 
ges           | Gender                      | Nominal 1 = male; 2=female
std           | Field of Study              | Nominal 1 = psychology; 2 = erziehungsw.; 3 = Lehramt; 4 = other
block         | Block Number                | Nominal 1 = instruction; 2 & 3 = training; 4-6 = testing
trg           | Overall trial number        | Integer
trial         | Trial number                | Integer
stnr          | ?                           | Integer
stim          | stimulus show in trial      | Nominal - even = Dogs, odd = Donuts, 01 = blue square, 02 = orange square
sneu          |  ??                         | ?
kat           | Category of stimulus        | Nominal  0 = square, 1 = donut, 2 = dog
stop          | Stop-trial or not           | Nominal 0 = no, 1 = yes 
ssd           | Stop-signal delay           | Integer 0,100,200 ms 
rgf           | response                    | Nominal 120 = left,right or nothing; Squares 1 = left, 2 = right ; DD  3 = left, 4 = right
resp          | given response              | Nominal 0 = nothing; Squares: 1 = left, 2 = right ; DD:  3 = left, 4 = right
fehl          | error                       | Nominal 0 = no, 1 = yes 
eff           | effect sound                | Nominal 0 = high/no-response sound, 12 = deep/response sound 
krit          | Critical trial or not       | Nominal 0 = no, 1 = yes 
feed          | Wrong or right feedback     | Nominal 0 = no feedback, 1 = right feedback, 2 = wrong feedback
rt            | reaction time               | Integer
verp          | misses                      | Integer 
iti           | true inter trial interval   | Integer  ~ 1100 ms 
ssd           | true Stop-signal delay      | Integer  ~ 0,100,200 ms
datum         | date                        | string 



## Trial informations

Next, I create three new variables, lag_crit, lag_error and lag_feed, where the entries of the krit,fehl and feed variables are shifted by one row, so I have the indication of the feedback type, if it is a critical trial and if the trial before was wrong, in the same row as the actual trial. At the end, I transform the feedback and block variables into  factors. 

```{r}

inhib <- inhib %>% dplyr::select(.,-trg,-trial,-stnr,-sneu, -iti,-datum) %>% 
                  mutate(., lag_crit = lag(krit) + 0,
                            lag_feed = lag(feed) + 0,
                            lag_error= lag(fehl) + 0,
                            lag_stop = lag(stop) + 0) %>% 
                  dplyr::select(.,vp,alt,std,ges,block,rgf,res,stop,kat,krit,ssd,
                                  fehl,lag_feed,lag_crit,lag_error,lag_stop,rt) %>% 
                  mutate(.,feed.f=factor(lag_feed,levels=c(0,1,2),
                                         labels=c("normal","right feedback","wrong feedback")),
                           block.f=factor(block))



inhib %>%   group_by(vp,block.f) %>% summarise(., trials = length(res),
                                                        squareTrials = sum(kat==0),
                                                        catTrials = sum(kat!=0),
                                                        criticaltrials = sum(krit==1),
                                                        lagcriticaltrials = sum(lag_crit==1),
                                                        errors = sum(fehl==1),
                                                        stopTrial = sum(stop==1),
                                                        critStop = sum(stop==1 & krit==1),
                                                        noncritStop = sum(stop==1 & krit==0)
                                                        )  


```

We want to exclude those trials, where the critical square trial and the categorization trial fall into different blocks. Number of trials now:  `r nrow(inhib)`. 

```{r}
inhib <- inhib %>% mutate(., lag_crit_block = lag(block)) %>% filter(., !(lag_crit==1 & block!=lag_crit_block))
```

New number of trials: `r nrow(inhib)`.

### How many stop trials are also critical trials? 

```{r}

test <- filter(inhib, block == 4 | block == 5 | block == 6)
table("stop"=test$stop,"krit"=test$krit)
```

Every critical trial is a stop trial. 

### Error Rates

I will only include the blocks 4,5 and 6. 

Error rates for each participant:

```{r}
(errorRates <- inhib %>% filter(., block == 4 | block == 5 | block == 6) %>% group_by(vp) %>% 
                                summarise(., Ntrials = length(res),
                                             Nerrors = sum(fehl==1),
                                             ErrorTrials =  Nerrors/Ntrials,
                                             Ncrit   = sum(lag_crit==1),
                                             ErrorCrit = sum(lag_crit==1 & lag_error==1)/Ncrit,
                                             Nsquare = sum(kat==0),
                                             ErrorSquare = sum(kat==0 & fehl==1)/Nsquare,
                                             Nstop   = sum(stop==1),
                                             Nstop100  = sum(stop==1 & ssd==100),
                                             Nstop200  = sum(stop==1 & ssd==200),
                                             ErrorStop = sum(stop==1 & fehl==1)/Nstop,
                                             ErrorStop100 = sum(stop==1 & fehl==1 & ssd==100)/sum(stop==1& ssd==100),
                                             ErrorStop200 = sum(stop==1 & fehl==1 & ssd==200)/sum(stop==1& ssd==200),
                                          
                                             Ncat    = sum(kat!=0),
                                             ErrorCat =  sum(kat!=0 & fehl==1)/Ncat,
                                            ## RTs
                                             meanRT = mean(rt),
                                             medianRT = median(rt),
                                             diffMeanMedian = meanRT-medianRT) %>% round(.,2))

```

Aggregated  over all participants: 

```{r}
describe(errorRates) %>% as.data.frame() %>% select(.,mean,sd,median,min,max) %>% round(.,2) %>% knitr::kable(.)
```

### Exclusion of VPN with error rates > 15 % 

```{r}
filter_vp <- filter(errorRates,ErrorTrials > 0.15) %>% select(.,vp)
inhib <- inhib[!(inhib$vp %in% filter_vp$vp),]
```


#### Updated Error Rates

```{r}
errorRates <- inhib %>% filter(., block == 4 | block == 5 | block == 6) %>% group_by(vp) %>% 
                                summarise(., Ntrials = length(res),
                                             Nerrors = sum(fehl==1),
                                             ErrorTrials =  Nerrors/Ntrials,
                                             Ncrit   = sum(lag_crit==1),
                                             ErrorCrit = sum(lag_crit==1 & lag_error==1)/Ncrit,
                                             Nsquare = sum(kat==0),
                                             ErrorSquare = sum(kat==0 & fehl==1)/Nsquare,
                                             Nstop   = sum(stop==1),
                                             Nstop100  = sum(stop==1 & ssd==100),
                                             Nstop200  = sum(stop==1 & ssd==200),
                                             ErrorStop = sum(stop==1 & fehl==1)/Nstop,
                                             ErrorStop100 = sum(stop==1 & fehl==1 & ssd==100)/sum(stop==1& ssd==100),
                                             ErrorStop200 = sum(stop==1 & fehl==1 & ssd==200)/sum(stop==1& ssd==200),
                                          
                                             Ncat    = sum(kat!=0),
                                             ErrorCat =  sum(kat!=0 & fehl==1)/Ncat,
                                            ## RTs
                                             meanRT = mean(rt),
                                             medianRT = median(rt),
                                             diffMeanMedian = meanRT-medianRT) 


describe(errorRates) %>% as.data.frame() %>% select(.,mean,sd,median,min,max) %>% round(.,2) %>% knitr::kable(.)
```

### Plot Error Distributions

```{r}
errorRates %>% select(.,  starts_with("Error")) %>% gather() %>% dplyr::rename(.,Errors=key) %>%
   ggplot(., aes(x=value*100, fill=Errors)) +
          geom_density(col=NA,alpha=0.5) +
          geom_rug(aes( y = 0,colour=Errors), position = position_jitter(height = 0),size = 1, show.legend = FALSE) +
          xlim(c(0,50)) +
          ggtitle("Distributions of Error Rates Accros Participants") +
          theme_bw() + 
          labs(
            #title = "Hitrate",
            x = " % Error Rate",
            y = "Frequency",
            color = NULL
          )

# ggsave("ErrorDistributuons.png",dpi=900,width=15,height=6, units = "cm",bg = "transparent")


errorRates %>% select(.,  starts_with("Error")) %>% gather() %>% dplyr::rename(.,Errors=key) %>%
   ggplot(.) +
          geom_density(aes(x=value*100)) +
          geom_rug(aes(x=value*100,y = 0), position = position_jitter(height = 0),size = 1, show.legend = FALSE) +
          ggtitle("Distributions of Error Rates Accros Participants") +
          theme_bw() + 
          labs(
            #title = "Hitrate",
            x = " % Error Rate",
            y = "Frequency",
            color = NULL
          ) +  facet_wrap(~Errors)


```


## Analysis


First, I filter only for those trials in the experimental blocks 4-6 were the stimulus was a dog or a donut

```{r}
inhib_crit <-  filter(inhib, block == 4 | block == 5 | block == 6, kat == 1 | kat == 2)
```



### Error Rates (for blocks 4,5 and 6 only)

Here we see the number of critical trials, errors and some RT descriptives per person 
```{r}
inhib_crit %>% group_by(vp) %>% summarise(., trials = length(res),
                                             criticaltrials = sum(lag_crit==1),
                                             errors = sum(fehl==1),
                                             lag_errors = sum(lag_error==1),
                                             errorrate = errors/trials,
                                             meanRT = mean(rt),
                                             medianRT = median(rt),
                                             diffMeanMedian = meanRT-medianRT)

```

and aggregated over all persons.

```{r}
inhib_crit %>% group_by(vp) %>% summarise(., trials = length(res),
                                             criticaltrials = sum(lag_crit==1),
                                             errors = sum(fehl==1),
                                             lage_errors=sum(lag_error==1),
                                             errorrate = errors/criticaltrials,
                                             meanRT = mean(rt),
                                             medianRT = median(rt),
                                             diffMeanMedian = meanRT-medianRT) %>%
  
                                        summarise(., meanT = mean(trials), 
                                                     meanCT = mean(criticaltrials)
                                                     )
```


<!-- There are some people with a high error rate (>10 %) even in this easy task. I will exclude all participants with an error rate > 10 %. -->

<!-- ```{r} -->
<!-- inhib_crit <- filter(inhib_crit,vp !=3 & vp != 6 & vp != 18) -->
<!-- ``` -->

#### Updated Demographics: 

```{r}
demo <- inhib %>% dplyr::select(.,vp,alt,ges,std) %>% group_by(.,vp)  %>% 
       # filter(.,vp !=3 & vp != 6 & vp != 18) %>%   
        summarise(age = mean(alt, na.rm = T),
                  gender = mean(ges, na.rm = T),
                  std = mean(std, na.rm = T)) %>% 
        mutate(., gender.f = factor(gender,labels=c("male","female","NA"),levels=c(1,2,9)), 
                  std.f = factor(std,labels=c("psychology","erziehungswiss","lehramt","other","NA"),
                            levels=c(1,2,3,4,9)))
  

psych::describe(demo$age) %>% knitr::kable()
table(demo$gender.f)
```



#### Looking at the errors people made: 

```{r}
filter(inhib_crit,fehl==1)
```


There are a lot of errors where people didn't press any button and therefore get an reaction time == 0. Therefore, I will exclude all trials with errors. I will also exclude all critical trials were the square trial before was answered wrong, because then the "wrong" feedback isn't wrong anymore. 

```{r}


inhib_crit_we <- filter(inhib_crit,fehl==0 & lag_error==0)
```

Critical trials, errors and mean & median RT per person:

```{r}
inhib_crit_we %>% group_by(vp) %>% summarise(., trials = length(res),
                                             criticaltrials = sum(lag_crit==1),
                                             errors = sum(fehl==1),
                                             lage_errors=sum(lag_error==1),
                                             errorrate = errors/criticaltrials,
                                             meanRT = mean(rt),
                                             medianRT = median(rt),
                                             diffMeanMedian = meanRT-medianRT)

```


and over all persons:

```{r}
inhib_crit_we %>% group_by(vp) %>% summarise(., trials = length(res),
                                             criticaltrials = sum(lag_crit==1),
                                             errors = sum(fehl==1),
                                             lage_errors=sum(lag_error==1),
                                             errorrate = errors/criticaltrials,
                                             meanRT = mean(rt),
                                             medianRT = median(rt),
                                             diffMeanMedian = meanRT-medianRT) %>%
  
                                        summarise(., meanNumberOfTrials = mean(trials), 
                                                     meanNumberOfCriticalTrials = mean(criticaltrials),
                                                     sd = sd(criticaltrials)
                                                     )
                                        
```


### Within-ANOVA

#### Descriptives

```{r}
inhib_crit_we %>% group_by(feed.f) %>%
        dplyr::summarize(.,  meanRT   = mean(rt),
                             medianRT = median(rt),
                             sdRT    = sd(rt))

inhib_crit_we %>% group_by(feed.f,block.f) %>%
        dplyr::summarize(.,  meanRT   = mean(rt),
                             medianRT = median(rt),
                             sdRT    = sd(rt))

```


```{r}


plotDF <- inhib_crit_we %>% group_by(vp,feed.f) %>% 
  dplyr::summarize(.,  meanRT   = mean(rt))


  ggplot(plotDF, aes(x=meanRT, fill=feed.f)) +
          geom_density(col=NA,alpha=0.4) +
          ggtitle("Distributions of RT (ms)")
  
  
  ggplot(plotDF, aes(y=meanRT, x=feed.f,fill=feed.f)) +
          geom_violin(col=NA,alpha=0.4) +
          ggtitle("Distributions of RT (ms)")

```


#### ANOVA

##### Aggregated By Mean 

```{r}
mod <- aov_car(rt ~ feed.f + Error(vp/feed.f),data=inhib_crit_we,fun_aggregate = mean)
knitr::kable(nice(mod))

summary(mod)

# get the least square means
referenceGrid <- emmeans(mod, ~ feed.f)

# pairwise comparisons
summary(pairs(referenceGrid, adjust="bonferroni")) %>%  knitr::kable(.)

# With Block as Factor 
mod <- aov_car(rt ~ feed.f + block.f + Error(vp/feed.f+block.f),data=inhib_crit_we,fun_aggregate = mean)
knitr::kable(nice(mod))

summary(mod)

# get the least square means
referenceGrid <- emmeans(mod, ~ feed.f * block.f)

# pairwise comparisons
summary(pairs(referenceGrid, adjust="bonferroni")) %>%  knitr::kable(.)

```

##### Aggregated By Median

```{r}
mod <- aov_car(rt ~ feed.f + Error(vp/feed.f),data=inhib_crit_we,fun_aggregate = median)
knitr::kable(nice(mod))

summary(mod)

# get the least square means
referenceGrid <- emmeans(mod, ~ feed.f)

# pairwise comparisons
summary(pairs(referenceGrid, adjust="bonferroni")) %>%  knitr::kable(.)

# With Block as Factor 
mod <- aov_car(rt ~ feed.f + block.f + Error(vp/feed.f+block.f),data=inhib_crit_we,fun_aggregate = median)
knitr::kable(nice(mod))
```



#### Plots

```{r}
id <- inhib_crit_we  %>% group_by(.,feed.f) %>%
              dplyr::summarize(., mean    = mean(rt),
                                  se      = sd(rt)/sqrt(length(rt)))


a <- inhib_crit_we  %>% group_by(.,feed.f,vp) %>%
             dplyr::summarize(., mean    = mean(rt),
                                  se      = sd(rt)/sqrt(length(rt)))


pd <- position_dodge(0.4)


ggplot(id, aes(x=feed.f, y=mean, fill=feed.f)) +
    geom_bar(position=position_dodge(), stat="identity") +
    #scale_fill_manual(values=c("grey80","grey70","grey60")) +
    scale_y_continuous(expand=c(0,0), limits = c(0, 800) ) +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))  +
    geom_line(data=a,  aes(x=feed.f, y=mean, group=vp),alpha = .3,lineend = "round",position = pd) +
    geom_point(data=a, aes(x=feed.f, y=mean,group=vp),shape = 21, alpha = .3,position = pd) +
     theme_bw() + theme(legend.position="none") + 
        labs(
          #title = "Hitrate",
          x = "Feedback type",
          y = "RT (ms)",
          color = NULL
        )


ggplot(id, aes(x=feed.f, y=mean,group=1)) +
     geom_smooth(method="loess") +
     geom_point() +
     scale_y_continuous(expand=c(0,0), limits = c(500,650) )  +
     geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2) + 
    theme_bw() + theme(legend.position="none") + 
          labs(
            #title = "Hitrate",
            x = "Feedback type",
            y = "RT (ms)",
            color = NULL
          )


ggplot(id, aes(x=feed.f, y=mean,group=1)) +
     geom_smooth(method="loess") +
     geom_point() +
     scale_y_continuous(expand=c(0,0), limits = c(480, 720) ) +
     geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, height = .2, position=position_dodge(.9))  +
     geom_line(data=a,  aes(x=feed.f, y=mean, group=vp),alpha = .3,lineend = "round",position = pd) +
     geom_point(data=a, aes(x=feed.f, y=mean,group=vp),shape = 21, alpha = .3,position = pd) +
     theme_bw() + theme(legend.position="none") + 
        labs(
          #title = "Hitrate",
          x = "Feedback type",
          y = "RT (ms)",
          color = NULL
        )

ggsave("plotResults.png",dpi=900,width=12,height=6, units = "cm",bg = "transparent")




id <- inhib_crit_we  %>% group_by(.,feed.f,block.f) %>%
              dplyr::summarize(., mean    = mean(rt),
                                  se      = sd(rt)/sqrt(length(rt)))


a <- inhib_crit_we  %>% group_by(.,feed.f,vp,block.f) %>%
             dplyr::summarize(., mean    = mean(rt),
                                  se      = sd(rt)/sqrt(length(rt)))


levels(id$feed.f) <- c("normal","right","wrong")
levels(id$block.f) <- c("Block 1","Block 2","Block 3","Block 4","Block 5","Block 6")

levels(a$feed.f) <- c("normal","right","wrong")
levels(a$block.f) <- c("Block 1","Block 2","Block 3","Block 4","Block 5","Block 6")


ggplot(id, aes(x=feed.f, y=mean,group=1)) +
     geom_smooth(method="loess") +
     geom_point() +
     scale_y_continuous(expand=c(0,0), limits = c(480, 720) ) +
     geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, height = .2, position=position_dodge(.9)) +
     geom_line(data=a,  aes(x=feed.f, y=mean, group=vp),alpha = .3,lineend = "round",position = pd) +
     geom_point(data=a, aes(x=feed.f, y=mean,group=vp),shape = 21, alpha = .3,position = pd) +
     theme_bw() + theme(legend.position="none") + 
        labs(
          #title = "Hitrate",
          x = "Feedback type",
          y = "RT (ms)",
          color = NULL
        ) +
  facet_grid(.~block.f)

ggsave("plotResultsInteraktion.png",dpi=900,width=15,height=6, units = "cm",bg = "transparent")


```


ANOVA only for block 4 


```{r}

block4 <- filter(inhib_crit_we, block==4)

mod <- aov_car(rt ~ feed.f + Error(vp/feed.f),data=block4,fun_aggregate = mean)
knitr::kable(nice(mod))

summary(mod)

# get the least square means
referenceGrid <- emmeans(mod, ~ feed.f)





block4_r_w <- filter(block4 , feed.f=="wrong feedback" |  feed.f=="right feedback")

aggr_data <- block4_r_w %>% group_by(.,vp,feed.f) %>% summarize(mRT=mean(rt))

leveneTest(mRT ~ feed.f,data=aggr_data)
t.test(mRT ~ feed.f,data=aggr_data,paired=TRUE,equal.var=TRUE,alternative ="less")

library(effsize)
wr <- filter(aggr_data,feed.f=="wrong feedback")
rg <- filter(aggr_data,feed.f=="right feedback")
cohen.d(rg$mRT,wr$mRT,data=aggr_data,paired=TRUE)



data <- block4 %>% dplyr::select(.,vp,rt,feed.f) %>% group_by(feed.f,vp) %>% summarize(., mRT=mean(rt)) %>% spread(feed.f,mRT) %>% write.csv2(file="KogSemJasp.csv",.)

```





# Explorations 
## Logistic regression on errors


```{r}
block4 <- filter(inhib_crit, block==4)

tab <- table(inhib_crit$fehl,inhib_crit$feed.f)
tab
tab[2,]/tab[1,]

logmod_error <- glmer(fehl ~ feed.f  + (feed.f|vp),data=block4,family=binomial)
summary(logmod_error)



```


## EZ-Diffusion model

```{r}

get.vaTer <- function(Pc,VRT,MRT,s=0.1){
  
  s2=s^2 # default value of the scaling paramter == 0.1
  
  if(Pc==0)
    cat("Error PC == 0 !\n")
  if(Pc==0.5)
    cat("Error PC == 0.5 !\n")
  if(Pc==1)
    cat("Error PC == 1 !\n")
  
  
  L = qlogis(Pc) # calculate logit
  x = L*(L*Pc^2 - L*Pc + Pc - .5)/VRT
  v = sign(Pc-.5)*s*x^(1/4) # drift rate
  a = s2*L/v # boundary spereation
  y = -v*a/s2
  
  MDT = (a/(2*v))*(1-exp(y))/(1+exp(y))
  Ter = MRT - MDT # non decision time
  
  return(list("drift rate= "= v,
              "boundary spereration = " = a,
              "non decision time = " = Ter))
  

  
}


inhib_crit %>% group_by(feed.f) %>% summarize( ., trials = length(res),
                                                  errors=sum(fehl==1),
                                                  errorrate = errors/trials,
                                                  Pc = sum(fehl==0)/trials,
                                                  check = errorrate + Pc,
                                                  MRT  = mean(rt)/1000,
                                                  VRT = var(rt)/(1000^2))








# right 
get.vaTer(Pc=0.960,VRT=0.0189,MRT=0.592,s=0.1)

# wrong
get.vaTer(Pc=0.963,VRT=0.0165,MRT=0.598,s=0.1)

# normal
get.vaTer(Pc=0.964,VRT=0.0173,MRT=0.559,s=0.1)




temp <- inhib_crit %>% group_by(feed.f,vp) %>% summarize( ., trials = length(res),
                                                  errors=sum(fehl==1),
                                                  errorrate = errors/trials,
                                                  Pc = sum(fehl==0)/trials,
                                                  check = errorrate + Pc,
                                                  MRT  = mean(rt,na.rm=TRUE)/1000,
                                                  VRT = var(rt)/(1000^2))

ez <- get.vaTer(Pc=temp$Pc,VRT=temp$VRT,MRT=temp$MRT,s=0.1)

m_v <- lm(unlist(ez[1])  ~ temp$feed.f)
summary(m_v)


```

